---
title: "HW1_P8105"
author: "Sania Sheifuddin"
date: "2026-09-26"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Loading libraries for this experiment 
#PROBLEM 1
```{r}
library(tidyverse)
```

# The data in this dataset, including names / values of important variables

```{r}
data("penguins", package = "palmerpenguins")
names (penguins)
penguins = janitor::clean_names(penguins)
```

```{r}
penguins
```

```{r}
skimr::skim(penguins)
```
In this data set, the table contains the measurements of different penguin parts. This table contains `r nrow(penguins)` rows  and `r ncol(penguins)` columns. From the skimmer `r skimr::skim(penguins)` We can see flipper length which has a mean of 200.92 mm and a standard deviation of 14.062mm. The bill length has a mean of 43.92 mm and a standard deviation of 5.46 mm. 
```{r}
# There are 344 rows and 8 columns in the table with the data set
penguins
nrow(penguins)
ncol(penguins)
```

```{r Flipper length mean}
# Rounding to one decimal point for simplicity, mean found to be 200.9
round(mean(penguins$flipper_length_mm, na.rm = TRUE), 1)
```

The mean was found to be `r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 1)` mm
```{r}
# This scatter plot shows the bill length and adjacent flipper length for three different penguin species which are Adelie, Chinstrap, and Gentoo. 
library (tidyverse) 
flipper_bill_plot =
ggplot (penguins, aes(x = bill_length_mm, 
   y = flipper_length_mm, color = species)) +
   geom_point()
  flipper_bill_plot
  ggsave("flipper_bill_plot.pdf")
```

#PROBLEM 2

```{r}
penguins_df = tibble (
  norm_samp = rnorm(10, mean = 1),
  norm_samp_pos = norm_samp > 0, 
  vec_char = c ("My", "name", "is", "Sania", "and", "I", "am", "in", "epi", "department"),
  vec_factor = factor(c("a","b","c","a","b","c","a","b","c","a"))
)
```

```{r}
mean(pull(penguins_df, norm_samp))
mean(pull(penguins_df,norm_samp_pos))
mean(pull(penguins_df, vec_char))
mean(pull(penguins_df, vec_factor))
```

```{r results = 'hide'}
as.numeric(pull(penguins_df,norm_samp_pos))
as.numeric(pull(penguins_df, vec_char))
as.numeric(pull(penguins_df, vec_factor))
```

